---
title             : "O*Net Factor Analysis Project"
shorttitle        : "SIOP_FA"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

# Methods

## Participants

## Material

## Procedure

# Results

Maybe try hierarchical which 2 overaching factors with the "dimensions" under each). 

We are working on a factor analysis of the characteristics themselves. This is based on the larger number of items (97?) with an n of now 568. 

We tried different numbers of factors based on a scree plot suggesting we start at 8 factors. We printed only those loadings at .3 or higher to begin. Very few items loaded on more than 1 factor, and most loaded at .3+ on one factor. A few were negative. Need to think carefully about interpretation by exploring what the items themselves are.

Next - tried a 2 factor solution, wondering if items in the "context" and "activity" categories loaded as expected based on Onet categories. Again, most items loaded at .3+. The physical items generally loaded on factor 1.

```{r scree plot}

data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script

data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
data$Interpersonal <-   rowMeans(data[63:76], na.rm=TRUE)
data$Information.I <-   rowMeans(data[77:81], na.rm=TRUE)
data$Mental.P <-        rowMeans(data[82:91], na.rm=TRUE)
data$WorkOutput <-      rowMeans(data[92:100], na.rm=TRUE)
data$Interact.Others <- rowMeans(data[101:117], na.rm=TRUE)

library(psych)
forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
fa.parallel(forfa, n.obs=568)
```

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
