---
title: "Submission_ResourceCount"
output:
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, echo=FALSE}

knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
#knitr::opts_knit$set(root.dir=normalizePath('../'))
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

Next steps (thoughts from 8/24):
Want this to be a more traditional project: DVs engagement, burnout, stress. 
How to operationalize IVs of resources, challenges, hindrances. May want to only count it if they somewhat agree or strongly agree. Could do a count or a sum of these values. The moderator of job type may work well in this idea. 

Want to include idea of item level things in terms of agreement. decreasing bar graphs relative to SD. Maybe we just present SD or SE. Thinking on SD, but ensure we have sufficient numbers of people responding to the item. 
Want to get a total count.

Alicia reflection 9/1/22: It actually appears that there may be more here with the engagement variable when reviewing the correlations. Knit and reflect more on the paper with that outcome being of focus.

John-o:
maybe use this as basis for another SIOP - extent to which resources and challenges are viewed similarly and also associations with engagement, burnout, etc... this operationalization is different than previous SIOP so could submit anew. Also would need a different approach to "similarity" - would need to look at item level


```{r study1}

temp <- read.csv("..//JDRJournalSubmission//initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

x <- paste("item", sep="",1:404)
y <- t(temp[2,])
                                        ## decluttering Qualtrics excess
data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
colnames(data) <- x

incomplete <- read.csv("..//JDRJournalSubmission//inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]                                          

data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))

colnames(data3) <- x

rm(x, y, temp)       

use <- rbind(data,data3)

## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)

library(careless)
use$careless_long <- longstring(use[18:399])
use$missing <- rowSums(is.na(use[18:404])) 

different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]

attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]

data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
data <- data[,c(1:404)]

numtot <- nrow(use)
numkicked <- nrow(different)
numvalid <- nrow(data)

```

```{r demos}

a <- descr::freq(use$item401, plot=FALSE)

use$item402[use$item402 == "Female " | use$item402 == "female" | use$item402 == "FEMALE" | use$item402 == "Woman" | use$item402 == "Mujer" | use$item402 == "feminine" | use$item402 == "fEMALE" | use$item402 == "F" | use$item402 == "Femenale" | use$item402 == "feminino" | use$item402 == "female " | use$item402 == "Fem" | use$item402 == "Feminine" | use$item402 == "feminine" | use$item402 == "WOMAN" | use$item402 == "Femal" | use$item402 == "femenine" | use$item402 == "Femenine" | use$item402 == "femenino" | use$item402 == "woman"]  <- "Female"

use$item402[use$item402 == "gerente" | use$item402 == "M" | use$item402 == "Make" | use$item402 == "Mal" | use$item402 == "male" | use$item402 == "MALE" | use$item402 == "male" | use$item402 == "Male" | use$item402 == "mals" | use$item402 == "man" | use$item402 == "masculine" | use$item402 == "Masculine" | use$item402 == "Man" | use$item402 == "mals " | use$item402 == "male " | use$item402 == "Male "]  <- "Male"

b <- descr::freq(use$item402, plot=FALSE)

##Job title
library(labourR)


#ESCO/ISCO classification using the labourR package
#ISCO = International Standard Classification of Occupations

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1) 

m3 <-merge(attention, ISCO, by.x = "id", by.y = "id", all.x = TRUE)

c <- descr::freq(m3$preferredLabel, plot=FALSE)

knowledge <- data[ which(m3$iscoGroup == "1" | m3$iscoGroup == "2"), ]
service <- data[ which(m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"), ]

data$item403[data$item403 == 2000]  <- 20

```


```{r generalrecodes, include=FALSE}

source("..//JDRJournalSubmission//recodescript.R", local = knitr::knit_global())

```

There were `r nrow(data)` retained respondents.

```{r keeping45}

## need to run "recodescript.R" prior to this if running chunk-by-chunk

## variables of interest (resource, challenge, hindrance): 118:372

library(dplyr)

data22 <- data %>% 
mutate_at(vars(118:372),
function(x) recode(x,
1==NA, 
2==NA,
3==NA,
4==4,
5==5))

## attention checks: 145, 248, 308

data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data22$item387 <- 7-data22$item387
data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

```

```{r matching}

## Trying to figure out which characteristics have agreement

## 145 & 248 (attention checks)
## maybe % match

data22$rh1  <- data22$item118 + data22$item203
data22$rh2  <- data22$item119 + data22$item204
data22$rh3  <- data22$item120 + data22$item205
data22$rh4  <- data22$item121 + data22$item206
data22$rh5  <- data22$item122 + data22$item207
data22$rh6  <- data22$item123 + data22$item208
data22$rh7  <- data22$item124 + data22$item209
data22$rh8  <- data22$item125 + data22$item210
data22$rh9  <- data22$item126 + data22$item211
data22$rh10 <- data22$item127 + data22$item212
data22$rh11  <- data22$item128 + data22$item213
data22$rh12  <- data22$item129 + data22$item214
data22$rh13  <- data22$item130 + data22$item215
data22$rh14  <- data22$item131 + data22$item216
data22$rh15  <- data22$item132 + data22$item217
data22$rh16  <- data22$item133 + data22$item218
data22$rh17  <- data22$item134 + data22$item219
data22$rh18  <- data22$item135 + data22$item220
data22$rh19  <- data22$item136 + data22$item221
data22$rh20  <- data22$item137 + data22$item222
data22$rh21  <- data22$item138 + data22$item223
data22$rh22  <- data22$item139 + data22$item224
data22$rh23  <- data22$item140 + data22$item225
data22$rh24  <- data22$item141 + data22$item226
data22$rh25  <- data22$item142 + data22$item227
data22$rh26  <- data22$item143 + data22$item228
data22$rh27  <- data22$item144 + data22$item229

data22$rh28  <- data22$item146 + data22$item230

data22$rh29  <- data22$item147 + data22$item231
data22$rh30  <- data22$item148 + data22$item232
data22$rh31  <- data22$item149 + data22$item233
data22$rh32  <- data22$item150 + data22$item234
data22$rh33  <- data22$item151 + data22$item235
data22$rh34  <- data22$item152 + data22$item236
data22$rh35  <- data22$item153 + data22$item237
data22$rh36  <- data22$item154 + data22$item238
data22$rh37  <- data22$item155 + data22$item239
data22$rh38  <- data22$item156 + data22$item240
data22$rh39  <- data22$item157 + data22$item241
data22$rh40  <- data22$item158 + data22$item242
data22$rh41  <- data22$item159 + data22$item243
data22$rh42  <- data22$item160 + data22$item244
data22$rh43  <- data22$item161 + data22$item245
data22$rh44  <- data22$item162 + data22$item246
data22$rh45  <- data22$item163 + data22$item247

data22$rh46  <- data22$item164 + data22$item249

data22$rh47  <- data22$item165 + data22$item250
data22$rh48  <- data22$item166 + data22$item251
data22$rh49  <- data22$item167 + data22$item252
data22$rh50  <- data22$item168 + data22$item253
data22$rh51  <- data22$item169 + data22$item254
data22$rh52  <- data22$item170 + data22$item255
data22$rh53  <- data22$item171 + data22$item256
data22$rh54  <- data22$item172 + data22$item257
data22$rh55  <- data22$item173 + data22$item258
data22$rh56  <- data22$item174 + data22$item259
data22$rh57  <- data22$item175 + data22$item260
data22$rh58  <- data22$item176 + data22$item261
data22$rh59  <- data22$item177 + data22$item262
data22$rh60  <- data22$item178 + data22$item263
data22$rh61  <- data22$item179 + data22$item264
data22$rh62  <- data22$item180 + data22$item265
data22$rh63  <- data22$item181 + data22$item266
data22$rh64  <- data22$item182 + data22$item267
data22$rh65  <- data22$item183 + data22$item268
data22$rh66  <- data22$item184 + data22$item269
data22$rh67  <- data22$item185 + data22$item270
data22$rh68  <- data22$item186 + data22$item271
data22$rh69  <- data22$item187 + data22$item272
data22$rh70  <- data22$item188 + data22$item273
data22$rh71  <- data22$item189 + data22$item274
data22$rh72  <- data22$item190 + data22$item275
data22$rh73  <- data22$item191 + data22$item276
data22$rh74  <- data22$item192 + data22$item277
data22$rh75  <- data22$item193 + data22$item278
data22$rh76  <- data22$item194 + data22$item279
data22$rh77  <- data22$item195 + data22$item280
data22$rh78  <- data22$item196 + data22$item281
data22$rh79  <- data22$item197 + data22$item282
data22$rh80  <- data22$item198 + data22$item283
data22$rh81  <- data22$item199 + data22$item284
data22$rh82  <- data22$item200 + data22$item285
data22$rh83  <- data22$item201 + data22$item286
data22$rh84  <- data22$item202 + data22$item287

###### Resource-Challenge:

data22$rc1  <- data22$item118 + data22$item288
data22$rc2  <- data22$item119 + data22$item289
data22$rc3  <- data22$item120 + data22$item290
data22$rc4  <- data22$item121 + data22$item291
data22$rc5  <- data22$item122 + data22$item292
data22$rc6  <- data22$item123 + data22$item293
data22$rc7  <- data22$item124 + data22$item294
data22$rc8  <- data22$item125 + data22$item295
data22$rc9  <- data22$item126 + data22$item296
data22$rc10 <- data22$item127 + data22$item297
data22$rc11  <- data22$item128 + data22$item298
data22$rc12  <- data22$item129 + data22$item299
data22$rc13  <- data22$item130 + data22$item300
data22$rc14  <- data22$item131 + data22$item301
data22$rc15  <- data22$item132 + data22$item302
data22$rc16  <- data22$item133 + data22$item303
data22$rc17  <- data22$item134 + data22$item304
data22$rc18  <- data22$item135 + data22$item305
data22$rc19  <- data22$item136 + data22$item306
data22$rc20  <- data22$item137 + data22$item307

data22$rc21  <- data22$item138 + data22$item309

data22$rc22  <- data22$item139 + data22$item310
data22$rc23  <- data22$item140 + data22$item311
data22$rc24  <- data22$item141 + data22$item312
data22$rc25  <- data22$item142 + data22$item313
data22$rc26  <- data22$item143 + data22$item314
data22$rc27  <- data22$item144 + data22$item315

data22$rc28  <- data22$item146 + data22$item316

data22$rc29  <- data22$item147 + data22$item317
data22$rc30  <- data22$item148 + data22$item318
data22$rc31  <- data22$item149 + data22$item319
data22$rc32  <- data22$item150 + data22$item320
data22$rc33  <- data22$item151 + data22$item321
data22$rc34  <- data22$item152 + data22$item322
data22$rc35  <- data22$item153 + data22$item323
data22$rc36  <- data22$item154 + data22$item324
data22$rc37  <- data22$item155 + data22$item325
data22$rc38  <- data22$item156 + data22$item326
data22$rc39  <- data22$item157 + data22$item327
data22$rc40  <- data22$item158 + data22$item328
data22$rc41  <- data22$item159 + data22$item329
data22$rc42  <- data22$item160 + data22$item330
data22$rc43  <- data22$item161 + data22$item331
data22$rc44  <- data22$item162 + data22$item332
data22$rc45  <- data22$item163 + data22$item333
data22$rc46  <- data22$item164 + data22$item334
data22$rc47  <- data22$item165 + data22$item335
data22$rc48  <- data22$item166 + data22$item336
data22$rc49  <- data22$item167 + data22$item337
data22$rc50  <- data22$item168 + data22$item338
data22$rc51  <- data22$item169 + data22$item339
data22$rc52  <- data22$item170 + data22$item340
data22$rc53  <- data22$item171 + data22$item341
data22$rc54  <- data22$item172 + data22$item342
data22$rc55  <- data22$item173 + data22$item343
data22$rc56  <- data22$item174 + data22$item344
data22$rc57  <- data22$item175 + data22$item345
data22$rc58  <- data22$item176 + data22$item346
data22$rc59  <- data22$item177 + data22$item347
data22$rc60  <- data22$item178 + data22$item348
data22$rc61  <- data22$item179 + data22$item349
data22$rc62  <- data22$item180 + data22$item350
data22$rc63  <- data22$item181 + data22$item351
data22$rc64  <- data22$item182 + data22$item352
data22$rc65  <- data22$item183 + data22$item353
data22$rc66  <- data22$item184 + data22$item354
data22$rc67  <- data22$item185 + data22$item355
data22$rc68  <- data22$item186 + data22$item356
data22$rc69  <- data22$item187 + data22$item357
data22$rc70  <- data22$item188 + data22$item358
data22$rc71  <- data22$item189 + data22$item359
data22$rc72  <- data22$item190 + data22$item360
data22$rc73  <- data22$item191 + data22$item361
data22$rc74  <- data22$item192 + data22$item362
data22$rc75  <- data22$item193 + data22$item363
data22$rc76  <- data22$item194 + data22$item364
data22$rc77  <- data22$item195 + data22$item365
data22$rc78  <- data22$item196 + data22$item366
data22$rc79  <- data22$item197 + data22$item367
data22$rc80  <- data22$item198 + data22$item368
data22$rc81  <- data22$item199 + data22$item369
data22$rc82  <- data22$item200 + data22$item370
data22$rc83  <- data22$item201 + data22$item371
data22$rc84  <- data22$item202 + data22$item372

####### Hindrance-Challenge

data22$hc1  <- data22$item203 + data22$item288
data22$hc2  <- data22$item204 + data22$item289
data22$hc3  <- data22$item205 + data22$item290
data22$hc4  <- data22$item206 + data22$item291
data22$hc5  <- data22$item207 + data22$item292
data22$hc6  <- data22$item208 + data22$item293
data22$hc7  <- data22$item209 + data22$item294
data22$hc8  <- data22$item210 + data22$item295
data22$hc9  <- data22$item211 + data22$item296
data22$hc10 <- data22$item212 + data22$item297
data22$hc11  <- data22$item213 + data22$item298
data22$hc12  <- data22$item214 + data22$item299
data22$hc13  <- data22$item215 + data22$item300
data22$hc14  <- data22$item216 + data22$item301
data22$hc15  <- data22$item217 + data22$item302
data22$hc16  <- data22$item218 + data22$item303
data22$hc17  <- data22$item219 + data22$item304
data22$hc18  <- data22$item220 + data22$item305
data22$hc19  <- data22$item221 + data22$item306
data22$hc20  <- data22$item222 + data22$item307

data22$hc21  <- data22$item223 + data22$item309

data22$hc22  <- data22$item224 + data22$item310
data22$hc23  <- data22$item225 + data22$item311
data22$hc24  <- data22$item226 + data22$item312
data22$hc25  <- data22$item227 + data22$item313
data22$hc26  <- data22$item228 + data22$item314
data22$hc27  <- data22$item229 + data22$item315
data22$hc28  <- data22$item230 + data22$item316
data22$hc29  <- data22$item231 + data22$item317
data22$hc30  <- data22$item232 + data22$item318
data22$hc31  <- data22$item233 + data22$item319
data22$hc32  <- data22$item234 + data22$item320
data22$hc33  <- data22$item235 + data22$item321
data22$hc34  <- data22$item236 + data22$item322
data22$hc35  <- data22$item237 + data22$item323
data22$hc36  <- data22$item238 + data22$item324
data22$hc37  <- data22$item239 + data22$item325
data22$hc38  <- data22$item240 + data22$item326
data22$hc39  <- data22$item241 + data22$item327
data22$hc40  <- data22$item242 + data22$item328
data22$hc41  <- data22$item243 + data22$item329
data22$hc42  <- data22$item244 + data22$item330
data22$hc43  <- data22$item245 + data22$item331
data22$hc44  <- data22$item246 + data22$item332
data22$hc45  <- data22$item247 + data22$item333

data22$hc46  <- data22$item249 + data22$item334

data22$hc47  <- data22$item250 + data22$item335
data22$hc48  <- data22$item251 + data22$item336
data22$hc49  <- data22$item252 + data22$item337
data22$hc50  <- data22$item253 + data22$item338
data22$hc51  <- data22$item254 + data22$item339
data22$hc52  <- data22$item255 + data22$item340
data22$hc53  <- data22$item256 + data22$item341
data22$hc54  <- data22$item257 + data22$item342
data22$hc55  <- data22$item258 + data22$item343
data22$hc56  <- data22$item259 + data22$item344
data22$hc57  <- data22$item260 + data22$item345
data22$hc58  <- data22$item261 + data22$item346
data22$hc59  <- data22$item262 + data22$item347
data22$hc60  <- data22$item263 + data22$item348
data22$hc61  <- data22$item264 + data22$item349
data22$hc62  <- data22$item265 + data22$item350
data22$hc63  <- data22$item266 + data22$item351
data22$hc64  <- data22$item267 + data22$item352
data22$hc65  <- data22$item268 + data22$item353
data22$hc66  <- data22$item269 + data22$item354
data22$hc67  <- data22$item270 + data22$item355
data22$hc68  <- data22$item271 + data22$item356
data22$hc69  <- data22$item272 + data22$item357
data22$hc70  <- data22$item273 + data22$item358
data22$hc71  <- data22$item274 + data22$item359
data22$hc72  <- data22$item275 + data22$item360
data22$hc73  <- data22$item276 + data22$item361
data22$hc74  <- data22$item277 + data22$item362
data22$hc75  <- data22$item278 + data22$item363
data22$hc76  <- data22$item279 + data22$item364
data22$hc77  <- data22$item280 + data22$item365
data22$hc78  <- data22$item281 + data22$item366
data22$hc79  <- data22$item282 + data22$item367
data22$hc80  <- data22$item283 + data22$item368
data22$hc81  <- data22$item284 + data22$item369
data22$hc82  <- data22$item285 + data22$item370
data22$hc83  <- data22$item286 + data22$item371
data22$hc84  <- data22$item287 + data22$item372

isolated <- data22[,c(22:32, 42:50, 52:60, 62:65, 67:117,411:662)]  ## characteristic ratings scattered because we didn't ask for resource/demand ratings for characteristics such as "exposure to radiation" - 9/12/22

```


```{r correlation_table, eval=FALSE}

r <- corx::corx(data22[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  escape = FALSE)

#cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

```


```{r regressions}

eng <- lm(engagement ~ hindrance + challenge + resource, data22)
bur <- lm(burnout ~ hindrance + challenge + resource, data22)
str <- lm(stress ~ hindrance + challenge + resource, data22)

summary(eng)
summary(bur)
summary(str)

```
